\LARGE \bf My Paper Title

### 2016-12-11 source/discussion/figures.tex
-- Refactored into separate files. -- Added another reference.
Referencing sections, tables, and figures
Added another image as a figure

% Define what kind of document we're going to write.
\documentclass[twocolumn]{article}

% For including images.
\usepackage{graphics}

% For including encapsulated postscript files.
\usepackage{epsfig}

% Needed to use the geometry command.
\usepackage{geometry}

% Set the size of the paper and the margins.
\geometry{letterpaper, portrait, margin=0.5in}

% Distance between columns.
\setlength{\columnsep}{0.4in}

% The package for the bibliography.
\usepackage{biblatex}

% The name of the bibliography file.
\addbibresource{references.bib}

% Set the title.
\title{\LARGE \bf My Paper Title}

% Set the author.
\author{Your Name Here}

% Start of the document.
\begin{document}

% Make the title
\maketitle

% Start of the abstract.
\begin{abstract}

% End of the abstract.
\end{abstract}

% New section.
\section{Introduction}
\label{sec:introduction}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
\cite{knuthwebsite}
All work and no play makes Jack a dull boy.

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

% New section.
\section{Details}
\label{sec:details}

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

% New sub-section.
\subsection{Figures}
\label{sec:details_figures}

% A figure.
\begin{figure}[h]
\centering
\includegraphics{../figures/shapes.eps}
\caption{These are some shapes.}
\label{fig:shapes}
\end{figure}

@@

% A figure.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/mountains.jpg}
\caption{Majestic mountains.}
\label{fig:mountains}
\end{figure}

% New sub-section.
\subsection{Bullets}
\label{sec:details_bullets}

% Start some bullets.
\begin{itemize}

\item All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

\item All work and no play makes Jack a dull boy.
All work and no play makes Jack a dull boy.

% End the bullets.
\end{itemize}

% New sub-section.
\subsection{Equations}
\label{sec:details_equations}

All work and no play makes Jack a dull boy.

$$
\alpha + \beta = \chi \eqno{(1)}
$$

% New sub-section.
\subsection{Tables}
\label{sec:details_tables}

@@

\begin{table}[h]
\caption{An Example of a Table}
\label{tab:table_a}
\begin{center}
\begin{tabular}{|c||c|c|}
\hline
One & Two & Three\\
\hline
Four & Five & Six\\
\hline
\end{tabular}
\end{center}
\end{table}

\section{Conclusion}
\label{sec:conclusions}

% New sub-section.
\subsection{Important Stuff}
\label{sec:conclusions_important_stuff}

\section*{Appendix}
\label{sec:appendix}

\section*{Acknowledgment}
\label{sec:acknowledgment}

% Generate the bibliography.
\printbibliography

% % Start of the bibliography.
% \begin{thebibliography}{99}

% \bibitem{c1} G. O. Young, Synthetic structure of industrial plastics (Book style with paper title and editor),   in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.

% \bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).  Belmont, CA: Wadsworth, 1993, pp. 123Ð135.

% \bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.

% \bibitem{c4} B. Smith, An approach to graphs of linear forms (Unpublished work style), unpublished.

% \bibitem{c5} E. H. Miller, A note on reflector arrays (Periodical styleÑAccepted for publication), IEEE Trans. Antennas Propagat., to be publised.

% % End of the bibliography.
% \end{thebibliography}

% End of the document.
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Copyright (c) 2016, Perry L Miller IV
%  All rights reserved.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  Discussion about figures.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Figures}
\label{sec:discussion_figures}

Good, then we will shall fight in the shade.
See figures
\ref{fig:shapes},
\ref{fig:mountains}, and
\ref{fig:lake} for details.
Good, then we will shall fight in the shade.

% A figure.
\begin{figure}[h]
\centering
\includegraphics{../figures/shapes.eps}
\caption{Made with LibreOffice and saved as EPS.}
\label{fig:shapes}
\end{figure}

@@

% A figure.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/mountains.jpg}
\caption{Misty Mountains from Unsplash It \cite{unsplash}.}
\label{fig:mountains}
\end{figure}

@@

% A figure.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth,natwidth=400,natheight=300]{../figures/lake.jpg}
\caption{A Mountain Lake from Unsplash It \cite{unsplash}.}
\label{fig:lake}
\end{figure}
